Integration of Multiple Constraints in ACG

### 2013-09-22 lenls/paper.tex
LENLS: Final remark from Maxime

We can observe another peculiarity on a more practical example. Consider the
G-ACG in Figure~\ref{fig:gacg}. In classical ACGs, one can always take an
element in a signature, like $Sem$, and by transduction find its corresponding
element in an another signature, like $Syntax$. However, in a G-ACG such as
this it, is possible that the $Syntax$ term we obtain by transduction does not
belong to $\mathcal{E}_{\mathcal{G}}(Syntax)$ because it lacks antecedents in
either $Constr_1$ or $Constr_2$. This means that the notion of an extrinsic
language is not capable to give us the set of all meaning terms in $Sem$ which
actually correspond to syntactically correct sentences in this G-ACG.

>>>>

We can observe another peculiarity on a more practical example. Consider the
G-ACG in Figure~\ref{fig:gacg}. In classical ACGs, one can always take an
element in a signature, like $Sem$, and by transduction find its corresponding
element in an another signature, like $Syntax$. However, in a G-ACG such as
this, it is possible that the $Syntax$ term we obtain by transduction does not
belong to $\mathcal{E}_{\mathcal{G}}(Syntax)$ because it lacks antecedents in
either $Constr_1$ or $Constr_2$. This means that the notion of an extrinsic
language is not capable to give us the set of all meaning terms in $Sem$ which
actually correspond to syntactically correct sentences in this G-ACG.
